---
title: "Reproducible Pitch Presentation"
author: "Jerin Rose"
date: "9/29/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Aim

Creating a Shiny application and deploy it on Rstudio's servers. Second,using Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about the application.

## Steps of follow

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

## How to use the application

This app gets the worker information

The application is running on 

[https://jerinrose.shinyapps.io/courseproject/](https://jerinrose.shinyapps.io/courseproject/)

The server.R and ui.R are in the repository

[https://github.com/Jerinrose/Reproducible_pitch ](https://github.com/Jerinrose/Reproducible_pitch)

## Plot

```{r,echo=F,message=FALSE,warning=FALSE}
library(plotly)
data<-read.csv("biostats.csv")

names(data)[names(data)=="Height..in."]<-"Height"
fig <- plot_ly(
  data, x = ~Age, y = ~Height,
  # Hover text:
  text = ~paste("Height:", Height, 'Age:', Age),
  color = ~Age, size = ~Age
)

fig
```